---
title: "NK Cell Project"
author: "Rüçhan Ekren"
date: "20/01/2021"
output:
  html_document:
    df_print: paged
---

We have a pre-processed and curated *Seurat* object of NK cells from 4 healthy donors(*HD*) and 4 Multiple Myeloma patients (*MM*).



First load up the required R packages,
```{r}
library(Seurat);library(ggplot2);library(patchwork);
```

Then let's read this object and see what it is consisted of.

```{r echo=TRUE}
nk <- readRDS("/home/ruchan/Desktop/work/RobjectsAndCo/NKonly.RDS")
nk
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
